### 2017-09-06 Documents/bootcamp_topic_intro.tex
Final edits

\begin{itemize}
\item  Today's handouts:  Syllabus, due dates, this outline, red/green stickers
\item  All posted on website (except the stickers).
\end{itemize}

@@

\section*{Setting up your computer}
\begin{itemize}
\item Create \verb|Data_Bootcamp| directory/folder on your computer. This is a place for you to save stuff to, work from, etc.
\item My style: To keep things simple I do the following
\begin{itemize}
\item Find your main hard drive, on PCs typically the ``C'' drive
\item In the C drive, create a folder called \verb|Data_Bootcamp|
\item Now if you every have to call this file you know it is \verb|c:\Data_Bootcamp|
\end{itemize}
\end{itemize}

@@

\section*{\href{https://github.com}{GitHub}}
\begin{itemize}
\item What I will use it for\ldots
\begin{itemize}
\item Source of ALL course materials
\item Place for you to grab materials on the fly. Save files by cut and paste, clever save as, or "Raw" (ask about this)
\end{itemize}
\item You need to create an account and email me your username
\item What you will use it for\ldots
\begin{itemize}
\item Post your homework and projects; I will ``pull'' them from there.
\item Long run: Think of this like an artists portfolio. Here you can post your code and projects and show potential employers, family, friends what you have done.
\end{itemize}
\item Now lets use it
\begin{itemize}
\item Create a new repository and name it \verb|my_first_repository|,
\item place the \verb|my_first_file.csv| file you created in it,
\item Great job! \\
Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
\end{itemize}
\end{itemize}

\section*{Anaconda}

>>>>

\begin{itemize}
\item  Today's handouts:  Syllabus, this outline, red/green stickers
\item  All posted on website (except the stickers).
\end{itemize}

@@

\section*{Setting up your computer}
\begin{itemize}
\item Create \verb|Data_Bootcamp| directory/folder on your computer. This is a place for you to save stuff to, work from, etc.
\item So do this\ldots
\begin{itemize}
\item Put red sticker on your laptop
\item Find your main hard drive, on PCs typically the ``C'' drive
\item In the C drive, create a folder called \verb|Data_Bootcamp|
\item Replace red sticker with green!
\end{itemize}
\item Now if you every have to call this file you know it is \verb|c:\Data_Bootcamp|
\end{itemize}

@@

\section*{\href{https://github.com}{GitHub}}
\begin{itemize}
\item What I will use it for\ldots
\begin{itemize}
\item Source of ALL course materials
\item Place for you to grab materials on the fly. Save files by cut and paste, clever save as, or "Raw" (ask about this)
\end{itemize}
\item You need to create an account and email me your username
\item What you will use it for\ldots
\begin{itemize}
\item Post your homework and projects; I will ``pull'' them from there.
\item Long run: Think of this like an artists portfolio. Here you can post your code and projects and show potential employers, family, friends what you have done.
\end{itemize}
\item Now lets use it
\begin{itemize}
\item Put red sticker on your laptop
\item Sign into github (if you do not have an account, create one)
\item Create a new repository and name it \verb|my_first_repository|,
\item place the \verb|my_first_file.csv| file you created in it,
\item Great job! Replace red sticker with green!\\
Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
\end{itemize}
\end{itemize}

\section*{\href{https://www.anaconda.com/download/}{Anaconda}}
